---
title: "Dynamic reporting of your SQL query entries"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output: html_document
params:
  analyte: str("")
  xlim: list()
  inputVal: NULL
  refInt: list()
  data: data.frame()
  ciTRUE: NULL
  ci: list(NA, NA, NA, NA)
  
---


```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(echo = FALSE)

# No sourcing of ouside ressources nessesary, because it is in the same envir! vERY SLICK :)

```

### Reference interval estimation  

Your reference interval is **`r round(params$refInt[1],2)`** - **`r round(params$refInt[2],2)`**. With confidence (`r paste0(round(params$ci[c(1,2)],3),collapse = "-")`) and (`r paste0(round(params$ci[c(3,4)],3),collapse = "-")`)

### Results 

You loaded **`r length(params$data$lab_value)` datapoints** from the analyte **`r params$analyte`**.


```{r, eval=FALSE, warning=TRUE, echo=FALSE, fig.height=3.5}

params$data$lab_value %>%
  as_tibble() %>%
  shinyHistogram(., ana = params$analyte, xlimits = params$xlim, 
                 inputVal = params$inputVal, 
                 refLower = params$refInt[1], refUpper = params$refInt[2],
                 ciTRUE = params$boostrapciTRUE,
                 ciLower=params$ci[c(1,2)],ciUpper=params$ci[c(3,4)]) 


```

This Report was generated using R Shiny, using `r sessionInfo()$platform` and running `r sessionInfo()$running`


```{r, eval=FALSE}
sessionInfo()
```
